### 2021-04-14 sections/model_overview/main.tex
Minor change

% PAR: COMBINED FORMULATION (Figure of 3-player game)
% Intro
Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
imperfect information extensive form game may arise. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players \cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each player chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen strategies are, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked.

@@

Based on the choice of strategy of these two players the distributor will then 
make its own choice of proportion of individuals to send to each system.

>>>>

Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
imperfect information extensive form game may arise. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players \cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each player chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen strategies are, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked.

@@

Based on the choice of strategy of these two players the distributor will then 
make its own choice of the proportion of individuals to send to each system.
